Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2014-02-27 tex/paper1/paper1.tex
more on the paper

\section{Observations}

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

@@

The arithmetic and geometric mean power spectra were formed from all
the time-series in each region.  A third power spectrum was created by
first summing all the data in a region, applying the
normalization/apodization procedure described above, and then
calculating the Fourier power spectrum.  These three power spectra
then summarize the Fourier power in each region, for each wavebad studied.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

\section{Helicity Amplitudes}

It has been realized that helicity amplitudes provide a convenient means
for Feynman diagram\footnote{Footnotes can be inserted like this.}
evaluations.  These amplitude-level techniques
are particularly convenient for calculations involving many Feynman
diagrams, where the usual trace techniques for the amplitude
squared becomes unwieldy.  Our calculations use the helicity techniques
developed by other authors \cite[]{hag86}; we briefly summarize below.

\subsection{Formalism} \label{bozomath}

%% The equation environment wil produce a numbered display equation.

A tree-level amplitude in $e^+e^-$ collisions can be expressed in
terms of fermion strings of the form
\begin{equation}
\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
\hat a_nu(p_1,\sigma_1) ,
\end{equation}
where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
four-momenta, gauge-boson polarization vectors or fermion strings with
an uncontracted Lorentz index associated with final-state fermions.

%% The \notetoeditor{TEXT} command allows the author to communicate
%% information to the copy editor.  This information will appear as a
%% footnote on the printed copy for the manuscript style file.  Nothing will
%% appear on the printed copy if the preprint or
%% preprint2 style files are used.

%% The eqnarray environment produces multi-line display math. The end of
%% each line is marked with a \\. Lines will be numbered unless the \\
%% is preceded by a \nonumber command.
%% Alignment points are marked by ampersands (&). There should be two
%% ampersands (&) per line.

In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
print} representation the $\gamma$ matrices are expressed
in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
\begin{eqnarray}
\gamma^\mu  & = &
 \left(
\begin{array}{cc}
0 & \sigma^\mu_+ \\
\sigma^\mu_- & 0
\end{array}     \right) ,
 \gamma^5= \left(
\begin{array}{cc}
-1 &   0\\
0 &   1
\end{array}     \right)  , \nonumber \\
\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
\end{eqnarray}
giving
\begin{equation}
\hat a= \left(
\begin{array}{cc}
0 & (\hat a)_+\\
(\hat a)_- & 0
\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
\end{equation}
The spinors are expressed in terms of two-component Weyl spinors as
\begin{equation}
u=\left(
\begin{array}{c}
(u)_-\\
(u)_+
\end{array}\right), v={\bf (}\vdag_+{\bf ,}   \vdag_-{\bf )} .
\end{equation}

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

The Weyl spinors are given in terms of helicity eigenstates
$\chi_\lambda(p)$ with $\lambda=\pm1$ by
\begin{mathletters}
\begin{eqnarray}
u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
_{-\lambda}(p)
\end{eqnarray}
\end{mathletters}

\section{Results}
\label{sec:results}
Figure \ref{}

%% This section contains more display math examples, including unnumbered
%% equations (displaymath environment). The last paragraph includes some
%% examples of in-line math featuring a couple of the AASTeX symbol macros.

\section{Coronal seismology and the effect of background assumptions}
\label{sec:corseis}

@@

Section \ref{sec:results} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{vaughan2010}.  Figure
\ref{fig:comparison}(b) shows that the assumption of a white-noise
background and a 95\% confidence level leads to the positive detection
of significant oscillatory power in this time series. Figure
\ref{fig:comparison}(c) shows that the assumption of a red-noise
background with the same confidence level significantly reduces the
area for which a detection may be claimed.  This simulated data, along
with the results of Section \ref{sec:results}, suggest that when
examining the wavelet transforms of time-seris for wave packets, a
background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying red-noise as evidence for an oscillatory
signal.

%% The displaymath environment will produce the same sort of equation as
%% the equation environment, except that the equation will not be numbered
%% by LaTeX.

Consider a task that computes profile parameters for a modified
Lorentzian of the form
\begin{equation}
I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
\end{equation}
where
\begin{displaymath}
d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
\end{array} \right) ^{2} +
\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
\end{displaymath}
\begin{displaymath}
d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
\end{array} \right) ^{2} +
\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
\end{displaymath}
\begin{displaymath}
x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
\end{displaymath}
\begin{displaymath}
y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
\end{displaymath}

In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
It is not clear how these sorts of analyses may affect determination of
 $M_{\sun}$, but the assumption is that the alternate results
should be less than 90\degr\ out of phase with previous values.
We have no observations of \ion{Ca}{2}.
Roughly \slantfrac{4}{5} of the electronically submitted abstracts
for AAS meetings are error-free.

@@

We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
doing the math in section~\ref{bozomath}.
More information on the AASTeX macros package is available \\ at
\url{http://www.aas.org/publications/aastex}.
For technical support, please write to
\email{aastex-help@aas.org}.

>>>>

\section{Observations}\label{sec:obs}

@@

The arithmetic and geometric mean power spectra were formed from all
the time-series in each region.  A third power spectrum was created by
first summing all the data in a region, applying the
normalization/apodization procedure described above, and then
calculating the Fourier power spectrum.  These three power spectra
then summarize the Fourier power in each region, for each wavebad
studied.  Figures \ref{fig:arith171} and \ref{fig:geom171} shows the
arithmetic and geometric mean power spectra for each region in AIA
171\AA.  Figures \ref{fig:arith193} and \ref{fig:geom193} show the
arithmetic and geometric mean power spectra for each region in AIA
193\AA.  Each mean power spectrum is also fit with a power spectrum of
the form
\begin{equation}
\label{eq:pwrlaw}
P(f) = Af^{-n} + C
\end{equation}
where $f$ is the frequency, $n$ is the power law index, $A$ a
normalization constant and $C$ is a background power.  Note that in
these plots, a least-squares fitting algorithm is used to fit this
model to the data.  The fit here is intended to show the approximate
power-law nature of the observed Fourier power spectrum.

\begin{figure}
\label{fig:arith171}

\caption{}
\end{figure}

\begin{figure}
\label{fig:geom171}

\caption{}
\end{figure}

\begin{figure}
\label{fig:arith193}

\caption{}
\end{figure}

\begin{figure}
\label{fig:geom193}

\caption{}
\end{figure}

\subsection{Initial inspection of the power spectra}\label{ssec:init}

\subsection{Comparing power spectra models}\label{ssec:twomodels}

\section{Discussion}
The presence of a power law Fourier spectrum in coronal emission poses
questions about how that emission is formed.  The power law power
spectrum also has implications for the detection of narrow frequency
band oscillations against such a background emission, which is the
purview of coronal seismology.  We discuss these two topics in the
sections below.

\subsection{Coronal seismology and the effect of background assumptions}
\label{ssec:corseis}

Section \ref{sec:results} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Coronal moss regions seem to show
slightly higher emission than a background power-law at a limited
range of frequencies.  However, this does not change the power-law
like nature of the emission - the power spectrum is essentially scale
free on average.  Therefore, on average, there is little guidance to
be had from coronal Fourier power spectra that can be used to pick a
time-scale that can be used to remove a background trend.

If there is no time-scale that can be used to remove a background
trend, then the time-series has to be analyzed without this processing
step.  Here too, the red-noise nature of the emission can cause
problems in attempting to analyze for the presence of narrow frequency
band oscillations.  Such oscillations are thought to be indicative of
waves in the solar atmosphere.

@@

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{vaughan2010}.  Figure
\ref{fig:comparison}(b) shows that the assumption of a white-noise
background and a 95\% confidence level leads to the positive detection
of significant oscillatory power in this time series. Figure
\ref{fig:comparison}(c) shows that the assumption of a red-noise
background with the same confidence level significantly reduces the
area for which a detection may be claimed.  This simulated data, along
with the results of Section \ref{sec:results}, suggest that when
examining the wavelet transforms of time-series for wave packets, a
background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying red-noise as evidence for an oscillatory
signal.

The foregoing discusses the implications of red-noise power spectra
for the detection of narrow-frequency band oscillations when looking
at single time-series.  The advantage of AIA is that there is more
than one time-series to consider.  Evidence for the presence of a wave
in the corona is much stronger if it can be shown that a narrow
frequency-band oscillation occurs is significantly above a red-noise
background signal in several neighboring pixels.

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}

\section{Conclusions}\label{sec:conc}

@@

We are grateful to the developers of SSWIDL \cite{}, SunPy \cite{},
PyMC \cite{} and matplotlib \cite{} for providing data preparation,
manipulation, analysis and display packages.  This work was supported
by the NASA....
